Blog post: Different map projections

### 2020-03-16 text/20/map-projections.Rmd
Added information about Colorado

```{r, echo=FALSE}
continental_us <- ggplot() + geom_sf(data = states)
projection_string <- "+proj=ortho +lon_0=-100 +lat_0=23.5 +ellps=WGS84 +no_defs"
states %>%
  filter(postal=="CO") %>%
  st_transform(projection_string) -> co
countries %>%
  ggplot() + 
  geom_sf(fill="white") + 
  geom_sf(data=co, color="red", fill="blue") +
  coord_sf(crs=projection_string)
```

>>>>

```{r, echo=FALSE}
continental_us <- ggplot() + geom_sf(data = states)
projection_string <- "+proj=ortho +lon_0=-80 +lat_0=23.5 +ellps=WGS84 +no_defs"
states %>%
  filter(postal=="CO") %>%
  st_transform(projection_string) -> co
countries %>%
  ggplot() + 
  geom_sf(fill="white") + 
  geom_sf(data=co, color="red", fill="white") +
  coord_sf(crs=projection_string)
```
